Use of significance test logic by scientists in a novel reasoning task

### 2019-08-06 inst/manuscript/manuscript.Rmd
Add project file, fix typo

Of the `r null_n` participants for whom the null hypothesis was true (i.e. $\delta=0$), `r t1_err_count` participants (`r round(t1_err_count/null_n * 100, 0)`%) incorrectly indicated an effect. This is larger than the typically-accepted 5% false positive rate in many sciences; however, participants were performing a novel task with no recourse to numbers or statistical software. Those who did not indicate an effect when $\delta=0$ tended to indicated that they *did not detect* an effect (`r null_nodet_count`; `r round(null_nodet_count/null_n * 100,0)`%), which is the correct conclusion from the SST perspective. The other `r null_same_count` (`r round(null_same_count/null_n * 100,0)`%) indicated that the groups were the same, which under SST is a fallacy.

>>>>

Of the `r null_n` participants for whom the null hypothesis was true (i.e. $\delta=0$), `r t1_err_count` participants (`r round(t1_err_count/null_n * 100, 0)`%) incorrectly indicated an effect. This is larger than the typically-accepted 5% false positive rate in many sciences; however, participants were performing a novel task with no recourse to numbers or statistical software. Those who did not indicate an effect when $\delta=0$ tended to indicate that they *did not detect* an effect (`r null_nodet_count`; `r round(null_nodet_count/null_n * 100,0)`%), which is the correct conclusion from the SST perspective. The other `r null_same_count` (`r round(null_same_count/null_n * 100,0)`%) indicated that the groups were the same, which under SST is a fallacy.
